Paradigms in Physics 2.0

### 2017-06-08 paper.tex
start work on pretty schedule figure

\begin{table*}[htbp]
\caption{Hypothetical student schedule for a student entering without
  calculus.  Students with AP Calculus can take the junior-year
  courses one year earlier, and students who start calculus-based
  physics in the Fall of their second year are not
  delayed.\label{schedule}}
\begin{ruledtabular}
\begin{tabular}{rlll}
  \textbf{Year} & \textbf{Fall} & \textbf{Winter} & \textbf{Spring} \\
  \hline
  1 & \mathcourse{Differential calculus}{251} &
  \mathcourse{Integral calculus}{252} &
  \mathcourse{Multivariable calculus}{254} \\
    & & \onecredit{Freshman Seminar} & \fourcredit{Calc Physics I} \\
\hline  2 & \mathcourse{Vector calculus}{255}
  & \mathcourse{Differential equations}{256}
  & \mathcourse{Linear algebra}{341} \\
  & \fourcredit{Calc Physics II} & \fourcredit{Calc Physics III} &\mathcourse{Series and
    sequences}{253} \\
  && \noted{Challenges}{3} & \noted{Theoretical Mechanics}{3}
  \\
\hline 3 & \paradigm{Quantum fundamentals} & \paradigm{Osciallations and waves} & \paradigm{Static fields}
\\
  & \paradigm{Energy and entropy} & \paradigm{Periodic systems} & \paradigm{Central forces}
\\
  & \onecredit{Computational lab I} & \onecredit{Computational lab II} & \onecredit{Computational lab III}
\\
  & \threecredit{Electronics} & \threecredit{Computer interfacing} & \onecredit{Research}
\\
\hline 4 & \capstone{Electromagnetism capstone} & \capstone{Quantum capstone} & \capstone{Thermal capstone}
\\
& \onecredit{Thesis} & \onecredit{Thesis} & \onecredit{Thesis}
\\
& \onecredit{Research} & \onecredit{Research}
\end{tabular}
\end{ruledtabular}
\end{table*}

\begin{table*}[htbp]
\caption{Hypothetical transfer student schedule.  Most transfer
  students will have a heavier schedule in their transfer year due
  to need to catch up on required math courses.\label{schedule}}
\begin{ruledtabular}
\begin{tabular}{rlll}
  \textbf{Year} & \textbf{Fall} & \textbf{Winter} & \textbf{Spring} \\
  \hline
3 & \paradigm{Quantum fundamentals} & \paradigm{Osciallations and waves} & \paradigm{Static fields}
\\
  & \paradigm{Energy and entropy} & \paradigm{Periodic systems} & \paradigm{Central forces}
\\
  & \onecredit{Computational lab I} & \onecredit{Computational lab II} & \onecredit{Computational lab III}
\\
  & \threecredit{Electronics} & \threecredit{Computer interfacing} & \onecredit{Research}
\\
& \mathcourse{Linear algebra}{341} & \noted{Challenges}{3} & \noted{Theoretical Mechanics}{3}
\\
&&\mathcourse{Vector calculus}{255}
\\
\hline 4 & \capstone{Electromagnetism capstone} & \capstone{Quantum capstone} & \capstone{Thermal capstone}
\\
& \onecredit{Thesis} & \onecredit{Thesis} & \onecredit{Thesis}
\\
& \onecredit{Research} & \onecredit{Research}
\end{tabular}
\end{ruledtabular}
\end{table*}

@@

\begin{figure}
%\includegraphics[width=0.8\linewidth]{figure1}
\caption{Figure captions appear below the figure while table captions appear above the table.\label{fig1}}
\end{figure}

>>>>

\begin{table*}[htbp]
\caption{Hypothetical student schedule for a student entering without
  calculus.  Students with AP Calculus can take the junior-year
  courses one year earlier, and students who start calculus-based
  physics in the Fall of their second year are not
  delayed.\label{schedule}}
\begin{ruledtabular}
\begin{tabular}{rlll}
  \textbf{Year} & \textbf{Fall} & \textbf{Winter} & \textbf{Spring} \\
  \hline
  1 & \mathcourse{Differential calculus}{251} &
  \mathcourse{Integral calculus}{252} &
  \mathcourse{Multivariable calculus}{254} \\
    & & \onecredit{Freshman Seminar} & \fourcredit{Calc Physics I} \\
\hline  2 & \mathcourse{Vector calculus}{255}
  & \mathcourse{Differential equations}{256}
  & \mathcourse{Linear algebra}{341} \\
  & \fourcredit{Calc Physics II} & \fourcredit{Calc Physics III} &\mathcourse{Series \&
    sequences}{253} \\
  && \noted{Challenges}{3} & \noted{Theoretical Mechanics}{3}
  \\
\hline 3 & \paradigm{Quantum fundamentals} & \paradigm{Osciallations \& waves} & \paradigm{Static fields}
\\
  & \paradigm{Energy \& entropy} & \paradigm{Periodic systems} & \paradigm{Central forces}
\\
  & \onecredit{Computational lab I} & \onecredit{Computational lab II} & \onecredit{Computational lab III}
\\
  & \threecredit{Electronics} & \threecredit{Computer interfacing} & \onecredit{Research}
\\
\hline 4 & \capstone{Electromagnetism capstone} & \capstone{Quantum capstone} & \capstone{Thermal capstone}
\\
& \onecredit{Thesis} & \onecredit{Thesis} & \onecredit{Thesis}
\\
& \onecredit{Research} & \onecredit{Research}
\end{tabular}
\end{ruledtabular}
\end{table*}

\begin{table*}[htbp]
\caption{Hypothetical transfer student schedule.  Most transfer
  students will have a heavier schedule in their transfer year due
  to need to catch up on required math courses.\label{schedule}}
\begin{ruledtabular}
\begin{tabular}{rlll}
  \textbf{Year} & \textbf{Fall} & \textbf{Winter} & \textbf{Spring} \\
  \hline
3 & \paradigm{Quantum fundamentals} & \paradigm{Osciallations \& waves} & \paradigm{Static fields}
\\
  & \paradigm{Energy \& entropy} & \paradigm{Periodic systems} & \paradigm{Central forces}
\\
  & \onecredit{Computational lab I} & \onecredit{Computational lab II} & \onecredit{Computational lab III}
\\
  & \threecredit{Electronics} & \threecredit{Computer interfacing} & \onecredit{Research}
\\
& \mathcourse{Linear algebra}{341} & \noted{Challenges}{3} & \noted{Theoretical Mechanics}{3}
\\
&&\mathcourse{Vector calculus}{255}
\\
\hline 4 & \capstone{Electromagnetism capstone} & \capstone{Quantum capstone} & \capstone{Thermal capstone}
\\
& \onecredit{Thesis} & \onecredit{Thesis} & \onecredit{Thesis}
\\
& \onecredit{Research} & \onecredit{Research}
\end{tabular}
\end{ruledtabular}
\end{table*}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{schedule}
\caption{Figure captions appear below the figure while table captions appear above the table.\label{fig1}}
\end{figure}
